Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-09-20 paper_comparison/paper_comparison/paper_comparison.Rmd
fix the table for example residual plots

@@

Other than checking diagnostic plots, analysts may perform formal hypothesis testing for detecting model defects. Depending on the alternative hypothesis that is focused on, a variety of tests can be applied. For example, the presence of heteroskedasticity can usually be tested by applying the White test [@white_heteroskedasticity-consistent_1980] or the Breusch-Pagan test [@breusch_simple_1979], which are both derived from the Lagrange multiplier test [@silvey1959lagrangian] principle that relies on the asymptotic properties of the null distribution. For testing non-linearity, one may apply the F-test to examine the significance of specific polynomial and non-linear forms of the regressors, or the significance of proxy variables as in the Ramsey Regression Equation Specification Error Test (RESET) [@ramsey_tests_1969]. And for testing normality, the Shapiro--Wilk test [ref here] is perhaps the most widely used test included by many of the statistical softwares. Another choice will be the Jarque--Bera test [ref here] which directly checks if the sample skewness and kurtosis match a normal distribution.

Example residual plots given in Figure \ref{fig:commondepartures} are examined by the corresponding F-test, Breusch-Pagan test and Shapiro--Wilk test as shown in Table \ref{tab:example-residual-plot-table}. In the example, both the Breusch-Pagan test and the Shapiro--Wilk test rejects the null hypothesis for departures they do not intend to examine. As discussed in @cook1982residuals, most residual-based tests for a particular type of departure from model assumptions are sensitive to other types of departures. It is likely the null hypothesis is correctly rejected but for the wrong reason, which is known as the "Type III error". Additionally, outliers will often incorrectly trigger the rejection of the null hypothesis despite the residuals are well-behaved [@cook_applied_1999]. This can be largely avoided in diagnostic plots as experienced analysts can evaluate the acceptability of assumptions flexibly, even in the presence of outliers.

<!-- report 0 when the value is small -->

<!-- F-test -> model structrual test -->

<!-- F-test -> F -->

<!-- right justified  -->

@@

<!-- red col -> bold -->

@@

data.frame(plot = c("B", "C", "D"), 
           model = c("Non-linearity", "Heteroskedasticity", "Non-normality"),
           f = c(POLY_MODEL$test(dat1)$p_value,
                 POLY_MODEL$test(mutate(dat2, z = poly_model()$gen(300, computed = select(dat2, x))$z))$p_value,
                 POLY_MODEL$test(mutate(dat3, z = poly_model()$gen(300, computed = select(dat3, x))$z))$p_value),
           b = c(HETER_MODEL$test(dat1)$p_value,
                 HETER_MODEL$test(dat2)$p_value,
                 HETER_MODEL$test(dat3)$p_value),
           s = c(shapiro.test(dat1$.resid)$p.value,
                 shapiro.test(dat2$.resid)$p.value,
                 shapiro.test(dat3$.resid)$p.value)) %>%
  mutate(f = format(f, digits = 2), b = format(b, digits = 2), s = format(s, digits = 2)) -> table_dat

  table_dat$f <- kableExtra::cell_spec(table_dat$f, color = ifelse(as.numeric(table_dat$f) < 0.05, "red", "black"))
  table_dat$b <- kableExtra::cell_spec(table_dat$b, color = ifelse(as.numeric(table_dat$b) < 0.05, "red", "black"))
  table_dat$s <- kableExtra::cell_spec(table_dat$s, color = ifelse(as.numeric(table_dat$s) < 0.05, "red", "black"))

  table_dat %>%
  knitr::kable(col.names = c("Residual plots", "Departures", "F-test ", "Breusch-Pagan test", "Shapiro–Wilk test"),
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Example residual plots examined by the corresponding conventional tests. P-values smaller than 0.05 are colored in red.', 
               label = "example-residual-plot-table" )

@@

<!-- Explain the tests you are showing later -->

<!-- -   RESET -->

<!-- -   BP -->

<!-- -   SW -->

<!-- and show the results for the residual plots displayed in previous section -->

<!-- Briefly mention any others  -->

@@

>>>>

(This section discusses the visual patterns data analysts expect to see and their implications.)

@@

(This section discusses the tests that will be used in the analysis and shows the results for the residual plots displayed in the previous section.)

Other than checking diagnostic plots, analysts may perform formal hypothesis testing for detecting model defects. Depending on the alternative hypothesis that is focused on, a variety of tests can be applied. For example, the presence of heteroskedasticity can usually be tested by applying the White test [@white_heteroskedasticity-consistent_1980] or the Breusch-Pagan test [@breusch_simple_1979], which are both derived from the Lagrange multiplier test [@silvey1959lagrangian] principle that relies on the asymptotic properties of the null distribution. For testing non-linearity, one may apply the F-test as a model structural test to examine the significance of specific polynomial and non-linear forms of the regressors, or the significance of proxy variables as in the Ramsey Regression Equation Specification Error Test (RESET) [@ramsey_tests_1969]. And for testing normality, the Shapiro--Wilk test [ref here] is perhaps the most widely used test included by many of the statistical softwares. Another choice will be the Jarque--Bera test [ref here] which directly checks if the sample skewness and kurtosis match a normal distribution.

Example residual plots given in Figure \ref{fig:commondepartures} are examined by the corresponding model structural test, Breusch-Pagan test and Shapiro--Wilk test as shown in Table \ref{tab:example-residual-plot-table}. In the example, both the Breusch-Pagan test and the Shapiro--Wilk test rejects the null hypothesis for departures that they do not intend to examine. As discussed in @cook1982residuals, most residual-based tests for a particular type of departure from model assumptions are sensitive to other types of departures. It is likely the null hypothesis is correctly rejected but for the wrong reason, which is known as the "Type III error". Additionally, outliers will often incorrectly trigger the rejection of the null hypothesis despite the residuals are well-behaved [@cook_applied_1999]. This can be largely avoided in diagnostic plots as experienced analysts can evaluate the acceptability of assumptions flexibly, even in the presence of outliers.

@@

@@

data.frame(plot = c("B", "C", "D"), 
           model = c("Non-linearity", "Heteroskedasticity", "Non-normality"),
           f = c(POLY_MODEL$test(dat1)$p_value,
                 POLY_MODEL$test(mutate(dat2, z = poly_model()$gen(300, computed = select(dat2, x))$z))$p_value,
                 POLY_MODEL$test(mutate(dat3, z = poly_model()$gen(300, computed = select(dat3, x))$z))$p_value),
           b = c(HETER_MODEL$test(dat1)$p_value,
                 HETER_MODEL$test(dat2)$p_value,
                 HETER_MODEL$test(dat3)$p_value),
           s = c(shapiro.test(dat1$.resid)$p.value,
                 shapiro.test(dat2$.resid)$p.value,
                 shapiro.test(dat3$.resid)$p.value)) %>%
  mutate(f = format(round(f, digits = 3), nsmall = 3), b = format(round(b, digits = 3), nsmall = 3), s = format(round(s, digits = 3), nsmall = 3)) -> table_dat

  table_dat$f <- kableExtra::cell_spec(table_dat$f, bold = as.numeric(table_dat$f) < 0.05)
  table_dat$b <- kableExtra::cell_spec(table_dat$b, bold = as.numeric(table_dat$b) < 0.05)
  table_dat$s <- kableExtra::cell_spec(table_dat$s, bold = as.numeric(table_dat$s) < 0.05)

  table_dat %>%
  knitr::kable(col.names = c("Residual plots", "Departures", "Model structural", "Breusch-Pagan", "Shapiro–Wilk"),
               align = "llrrr",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Example residual plots examined by the corresponding conventional tests. P-values smaller than 0.05 are colored in red.', 
               label = "example-residual-plot-table" )

@@

@@

(This sec)

### 2022-09-20 paper_comparison/paper_comparison/paper_comparison.tex
fix the table for example residual plots

Other than checking diagnostic plots, analysts may perform formal
hypothesis testing for detecting model defects. Depending on the
alternative hypothesis that is focused on, a variety of tests can be
applied. For example, the presence of heteroskedasticity can usually be
tested by applying the White test
\citep{white_heteroskedasticity-consistent_1980} or the Breusch-Pagan
test \citep{breusch_simple_1979}, which are both derived from the
Lagrange multiplier test \citep{silvey1959lagrangian} principle that
relies on the asymptotic properties of the null distribution. For
testing non-linearity, one may apply the F-test to examine the
significance of specific polynomial and non-linear forms of the
regressors, or the significance of proxy variables as in the Ramsey
Regression Equation Specification Error Test (RESET)
\citep{ramsey_tests_1969}. And for testing normality, the Shapiro--Wilk
test {[}ref here{]} is perhaps the most widely used test included by
many of the statistical softwares. Another choice will be the
Jarque--Bera test {[}ref here{]} which directly checks if the sample
skewness and kurtosis match a normal distribution.

Example residual plots given in Figure \ref{fig:commondepartures} are
examined by the corresponding F-test, Breusch-Pagan test and
Shapiro--Wilk test as shown in Table
\ref{tab:example-residual-plot-table}. In the example, both the
Breusch-Pagan test and the Shapiro--Wilk test rejects the null
hypothesis for departures they do not intend to examine. As discussed in
\citet{cook1982residuals}, most residual-based tests for a particular
type of departure from model assumptions are sensitive to other types of
departures. It is likely the null hypothesis is correctly rejected but
for the wrong reason, which is known as the ``Type III error''.
Additionally, outliers will often incorrectly trigger the rejection of
the null hypothesis despite the residuals are well-behaved
\citep{cook_applied_1999}. This can be largely avoided in diagnostic
plots as experienced analysts can evaluate the acceptability of
assumptions flexibly, even in the presence of outliers.

@@

\caption{\label{tab:example-residual-plot-table}Example residual plots examined by the corresponding conventional tests. P-values smaller than 0.05 are colored in red.}
\centering
\begin{tabular}[t]{lllll}
\toprule
Residual plots & Departures & F-test  & Breusch-Pagan test & Shapiro–Wilk test\\
\midrule
B & Non-linearity & \textcolor{red}{7.3e-117} & \textcolor{red}{1.8e-14} & \textcolor{red}{3.9e-02}\\
C & Heteroskedasticity & \textcolor{black}{ 3.8e-01} & \textcolor{red}{6.1e-16} & \textcolor{red}{1.1e-09}\\
D & Non-normality & \textcolor{black}{ 6.7e-01} & \textcolor{black}{7.4e-01} & \textcolor{red}{2.9e-18}\\
\bottomrule
\end{tabular}
\end{table}

>>>>

(This section discusses the tests that will be used in the analysis and
shows the results for the residual plots displayed in the previous
section.)

Other than checking diagnostic plots, analysts may perform formal
hypothesis testing for detecting model defects. Depending on the
alternative hypothesis that is focused on, a variety of tests can be
applied. For example, the presence of heteroskedasticity can usually be
tested by applying the White test
\citep{white_heteroskedasticity-consistent_1980} or the Breusch-Pagan
test \citep{breusch_simple_1979}, which are both derived from the
Lagrange multiplier test \citep{silvey1959lagrangian} principle that
relies on the asymptotic properties of the null distribution. For
testing non-linearity, one may apply the F-test as a model structural
test to examine the significance of specific polynomial and non-linear
forms of the regressors, or the significance of proxy variables as in
the Ramsey Regression Equation Specification Error Test (RESET)
\citep{ramsey_tests_1969}. And for testing normality, the Shapiro--Wilk
test {[}ref here{]} is perhaps the most widely used test included by
many of the statistical softwares. Another choice will be the
Jarque--Bera test {[}ref here{]} which directly checks if the sample
skewness and kurtosis match a normal distribution.

Example residual plots given in Figure \ref{fig:commondepartures} are
examined by the corresponding model structural test, Breusch-Pagan test
and Shapiro--Wilk test as shown in Table
\ref{tab:example-residual-plot-table}. In the example, both the
Breusch-Pagan test and the Shapiro--Wilk test rejects the null
hypothesis for departures that they do not intend to examine. As
discussed in \citet{cook1982residuals}, most residual-based tests for a
particular type of departure from model assumptions are sensitive to
other types of departures. It is likely the null hypothesis is correctly
rejected but for the wrong reason, which is known as the ``Type III
error''. Additionally, outliers will often incorrectly trigger the
rejection of the null hypothesis despite the residuals are well-behaved
\citep{cook_applied_1999}. This can be largely avoided in diagnostic
plots as experienced analysts can evaluate the acceptability of
assumptions flexibly, even in the presence of outliers.

@@

\caption{\label{tab:example-residual-plot-table}Example residual plots examined by the corresponding conventional tests. P-values smaller than 0.05 are colored in red.}
\centering
\begin{tabular}[t]{llrrr}
\toprule
Residual plots & Departures & Model structural & Breusch-Pagan & Shapiro–Wilk\\
\midrule
B & Non-linearity & \textbf{0.000} & \textbf{0.000} & \textbf{0.039}\\
C & Heteroskedasticity & 0.378 & \textbf{0.000} & \textbf{0.000}\\
D & Non-normality & 0.667 & 0.736 & \textbf{0.000}\\
\bottomrule
\end{tabular}
\end{table}
